Bird beak's elaboration and innovation

### 2022-10-25 Analysis/03.1-Elaboration_innovation_analysis[statistics].Rmd
Update 03.1-Elaboration_innovation_analysis[statistics].Rmd

```{r, echo = FALSE, eval = TRUE}
## Quick load
load(file = "../Data/Processed/shapespace_allbirds_lvl_superorder_order_results_list.rda")
results <- shapespace_allbirds_lvl_superorder_order_results_list
rm(shapespace_allbirds_lvl_superorder_order_results_list)

@@

## Distribution of elaboration and innovation at the group level
scale.group <- function(X) return(X/max(X))
elaboration_super_orders <- lapply(get.disparity(results$super_results_between$position, concatenate = FALSE), scale.group)
innovation_super_orders  <- lapply(get.disparity(results$super_results_between$distance, concatenate = FALSE), scale.group)
elaboration_orders       <- lapply(get.disparity(results$order_results_between$position, concatenate = FALSE), scale.group)
innovation_orders        <- lapply(get.disparity(results$order_results_between$position, concatenate = FALSE), scale.group)
elaboration_group <- rbind(do.call(rbind, elaboration_super_orders), do.call(rbind, elaboration_orders))
innovation_group <- rbind(do.call(rbind, innovation_super_orders), do.call(rbind, innovation_orders))

## Measuring the area under the curves
elaboration_species_auc <- apply(elaboration_species, 2, area.density)
innovation_species_auc <- apply(innovation_species, 2, area.density)
elaboration_group_auc <- apply(elaboration_group, 2, area.density)
innovation_group_auc <- apply(innovation_group, 2, area.density)

>>>>

```{r, echo = FALSE, eval = TRUE}
## Quick load
source("../Functions/stats.utilities.R")
library(dispRity)
load(file = "../Data/Processed/shapespace_allbirds_lvl_superorder_order_results_list.rda")
results <- shapespace_allbirds_lvl_superorder_order_results_list
rm(shapespace_allbirds_lvl_superorder_order_results_list)

@@

## Distribution of elaboration and innovation at the clade level
scale.group <- function(X) return(X/max(X))
elaboration_super_orders <- lapply(get.disparity(results$super_results_between$position, concatenate = FALSE), scale.group)
innovation_super_orders  <- lapply(get.disparity(results$super_results_between$distance, concatenate = FALSE), scale.group)
elaboration_orders       <- lapply(get.disparity(results$order_results_between$position, concatenate = FALSE), scale.group)
innovation_orders        <- lapply(get.disparity(results$order_results_between$distance, concatenate = FALSE), scale.group)
## The objects above are the ones that contain all the elaboration and innovation values by clade level

## These bits are for the Bhatt coeff
elaboration_group <- rbind(do.call(rbind, elaboration_super_orders), do.call(rbind, elaboration_orders))
innovation_group <- rbind(do.call(rbind, innovation_super_orders), do.call(rbind, innovation_orders))

## Measuring the area under the curves (for the Bhatt coeff)
elaboration_species_auc <- apply(elaboration_species, 2, area.density)
innovation_species_auc <- apply(innovation_species, 2, area.density)
elaboration_group_auc <- apply(elaboration_group, 2, area.density)
innovation_group_auc <- apply(innovation_group, 2, area.density)
